A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-13 docs/icccn2009/paper.tex
Added section on web interface
git-svn-id: svn://localhost/netbeams/trunk@384 559edde2-a4d4-44e0-96fc-4035e40d7396

Web Interface. Management messages are regular
DSPMessages. Asynchronous UI: UI may only build up after next
communication cycle.

>>>>

One of NetBEAMS goals is the ability to easily configure the sensor
network without programming skills. Technicians should be able to
change configuration parameters of various DSP Components via an
easy-to-use web interface. With regards to the NetBEAMS specific
components discussed in earlier sections, these configuration
parameters are for example the sampling frequency of the YSI Sonde DP
and the upload frequency of the the wire transport DC.

The way this configuration is done by a special DSP Component that
offers a web interface through which a technician can define the
configuration parameters (component \ding{197} in Figure
\ref{FIG_NETBEAMS}). The web management component first queries the remote
component to get a list of configuration parameters. Once the remote
component sends a reply, a user interface is automatically built up
to allow the entry of user defined values. When those values are
submitted, an update message is sent back to the remote component that
will then change the appropriate configuration parameters.

The user interface offered by the web management component is
asynchronous in the sense that there might be a time lag between a
request and a response. This has to do with the fact that the remote
DSP will only establish a communication link in certain time intervals
during which the query and update messages will be forwarded. Apart
from component configuration, the web management component is also
capable to remotely start, stop, and re-deploy new versions of DSP
Components.
